---
title: "newPredictionModel"
output: 
  html_document: 
    theme: journal
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data
```{r , echo=TRUE}
x <- c("Hello", "World")
y <- "Pizda"
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Get Current Weather Parametes

```{r , echo=FALSE, warning=FALSE}
getRecentWeatherData <- function () {
library("RMySQL");


# Create DB Connection ----------------------------------------------------

con <- dbConnect(MySQL(),
                 user = "read", 
                 host = "mikmak.cc",
                 password = "809913", 
                 db = "weatherDW");

# Get Recent MessageID ----------------------------------------------------

query <- dbSendQuery(con, statement = paste("SELECT MAX(recID) FROM log WHERE msgv1 = 'WAE' AND sysID = '79cf6c22-dcc6-11e5-8e77-00113217113f'"));
recID <- fetch(query)

queryStatement <- paste("SELECT logID FROM log WHERE recID = '", recID, "'", ssep = "")
query <- dbSendQuery(con, statement = queryStatement);
maxLogID <- fetch(query)

# Download Sensor Data ----------------------------------------------------
queryStatement <- paste("SELECT * FROM log WHERE logID ='", maxLogID, "'", sep = "" )
query <- dbSendQuery(con, statement = queryStatement)
#maxMsgID <- fetch(query, n = -1)
weatherData <- fetch(query)

dbDisconnect(con)

weatherData <- cbind(weatherData[,4], weatherData[,5])
weatherData <- (weatherData)
rownames(weatherData) <- weatherData[,1]
weatherData <- weatherData[,2]
#weatherData <- t(weatherData)

# 1. Temperature
# 2. Pressure
# 3. Wind
# 4. Rain
# 5. Humidity
weatherData <- rbind(weatherData[1], weatherData[2], weatherData[4], weatherData[5], weatherData[3])
rownames(weatherData) <- c("Temperature", "Pressure", "Wind", "Rain", "Humidity")
weatherData <- (weatherData)
return(weatherData)

}
```



```{r c(getRecentWeatherData), echo=TRUE, warning=FALSE}
actualTemperature <- getRecentWeatherData()

print(actualTemperature)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.





## Download Weather Data from DB (for this year)


## Transform Weather Data into Table


## Download Irrigation Log


## Summarise Irrigation on a day base (Night belongs to previous da


## Visualize Weather Data and Irrigatiion Log


## Try to predict wind and rain from weather of last 3 days


## Enhance previous year data with rain and wind data


## Merge Data into One Big DataSet


## Train NN to Predict Pump Duration


## Visualize Real Values vs. Predicted Values



