---
title: "TestPredictiveModel"
author: "mikmak"
date: "11 September 2016"
output: html_document
---

# Create Connection to DB

```{r con.iRig con.WeatherDW}
library("RMySQL");

# Create DB Connection ----------------------------------------------------

con.iRig <- dbConnect(MySQL(),
                 user = "read", 
                 host = "mikmak.cc",
                 password = "809913", 
                 db = "iRig");

con.weatherDW <- dbConnect(MySQL(),
                 user = "read", 
                 host = "mikmak.cc",
                 password = "809913", 
                 db = "weatherDW");
```

# Get Data
First get source data from DB, like Weather Log, Pump Log and Prediction Model.
All variables have prefix "e" indicating it is Entry Layer

```{r echo=FALSE}
# Get PumpLog
sql <- paste('SELECT MsgID, msgv1, TmStp FROM sysLog WHERE msgID = "109" AND sysID = "79cf6c22-dcc6-11e5-8e77-00113217113f"')
query <- dbSendQuery(con.iRig, statement = sql)
ePumpLog <- fetch(query, n=-1)

# Get WeatherLog
query <- dbSendQuery(con.weatherDW, statement = paste("SELECT msgID, msgv1, tmstp FROM log WHERE sysID = '79cf6c22-dcc6-11e5-8e77-00113217113f'"))
eWeatherLog <- fetch(query, n=-1)
#return(eWeatherLog)

# Get Predicitive Model
ePredictiveModel <- read.csv("data/iRigModel", sep="")

dbDisconnect(con.iRig)
dbDisconnect(con.weatherDW)

```

# Clean and Transform Data
Remove corupted or test data or data not needed for further analysis.
```{r}
tWeatherLog <- cbind(eWeatherLog[eWeatherLog$msgID == 801,c(3,2)], 
                     eWeatherLog[eWeatherLog$msgID == 802,2], 
                     eWeatherLog[eWeatherLog$msgID == 820,2],
                     eWeatherLog[eWeatherLog$msgID == 841,2],
                     eWeatherLog[eWeatherLog$msgID == 851,2],
                     eWeatherLog[eWeatherLog$msgID == 102,2],
                     eWeatherLog[eWeatherLog$msgID == 101,2])
colnames(tWeatherLog) <- c("TimeStamp", "Temperature", "Pressure", "Humidity", "Wind", "Rain", "DataTimeStamp", "Location")
tWeatherLog <- tWeatherLog[tWeatherLog$Location == "WAE",]

tWeatherLog[,1] <- as.POSIXct(tWeatherLog[,1], origin="1970-01-01")
tWeatherLog <- cbind(tWeatherLog, as.Date(tWeatherLog[,1]))

tWeatherLog <- tWeatherLog[order(tWeatherLog$TimeStamp),]

colnames(tWeatherLog) <- c("TimeStamp", "Temperature", "Pressure", "Humidity", "Wind", "Rain", "DataTimeStamp", "Location", "Date")

```

I started to record weather parameters on 27.7.2016. Therefore the pumpLog before this date is useless
```{r}
tPumpLog <- ePumpLog
tPumpLog[,3] <- as.POSIXct(tPumpLog[,3], origin="1970-01-01")
tPumpLog <- cbind(ePumpLog, as.Date(tPumpLog[,3]))
names(tPumpLog)[ncol(tPumpLog)] <- "Date"
tPumpLog <- tPumpLog[tPumpLog$Date >= min(tWeatherLog$Date),]
```


```{r, echo=FALSE}
plot(tWeatherLog[, c("TimeStamp", "Temperature")], type = "l")
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
